
```{r}
flavours <- tidy_whisky %>%
    distinct(flavour)

regional_palette <- tidy_whisky %>%
    group_by(Region, flavour) %>% 
summarise(average = mean(strength)) %>% 
    print()



```
Testing correlation between different flavours
```{r}
tidy_whisky %>%
    select(Region, flavour, strength) %>% 
    # pivot_wider(names_from = flavour, values_from = strength) %>% 
ggpairs(colour = "Region")


```



Testing negative correlation between smoky and floral, body and 
```{r}

```

```{r}
regional_palette %>%
    ggplot() +
    aes(x = region, y = smoky, fill = region) +
    geom_col()
```

Main Charts

selectinputs for multiple regional flavours - polygon
leaflet for regional distilleries
bar chart for each flavour dimension and regional selection


```{r}




```
secondary charts
preferred user flavour profile providing suggested whiskys
interactive scatter chart of distilleries x = 'delicateproxy to full bodied' y = smoky to 'not-smokyproxy'




```{r}

```

charts that need more consideration
latitude longitude for 'average' regional distillery location
'expected' flavour profiles with latitude / longitude